---
title: "R Notebook"
output:
  html_document:
    number_sections: yes
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---
# Introduction (including choice of data, questions), Team description

# Description of Data

We get the dataset from the Global Terrorism Database (GTD) http://start.umd.edu/gtd/, which is an open-source database including information on terrorist events around the world from 1970 through 2016 (with annual updates planned for the future). Unlike many other event databases, the GTD includes systematic data on domestic as well as international terrorist incidents that have occurred during this time period and now includes more than 170,000 cases. The dataset ends in 2016 because GTD collection beyond 2016 is ongoing and the website is updated annually. They expect to release the 2017 data in Summer 2018. 

In our project, we divide the whole dataset into two subgroups: the data in 1970 to 1974 and 2011-2016. We would like to carry out data visualizatioin and data analysis on these subgroups individually and compare their performances.

For the dataset from 1970-1974, there are 2670 observations of 135 variables. For the dataset from 2011-2016, there are 2670 observations of 135 variables.

The variables include

```{r}
library(openxlsx)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(rworldmap)
```

# Graphical Analysis of Data Quality

```{r}

terrorism <- read.xlsx("/Users/xiangyu/Documents/GitHub/EDAV_FinalProj/data/raw data/globalterrorismdb_0617dist.xlsx")

terrorism1<-terrorism[terrorism$iyear<=1974,]

write.csv(terrorism1,"terrorism1.csv")

terrorism2<-terrorism[terrorism$iyear>=2012,]

write.csv(terrorism2,"terrorism2.csv")
```


## discover what's in the data file that was exported
```{r}

## choose variables

```

## imputations for NULL values 
```{r}

```


## Outlier Analysis and Treatment
```{r}

```

# Main Analysis (focus on quality of EDA choices / techniques)


## countries with the most attack, 1970-1974; 2011-2016
```{r}

```


## Terrorist Attack Tactics Wordwide, 1970-1974; 2011-2016
```{r}

```

## Terrorist Attack By Weapon Wordwide, 1970-1974; 2011-2016
```{r}

```

## Casualties, 1970-1974; 2011-2016
```{r}

```


## Terrorist Attack Targets in 1970 and 2016

There are a lot of different terrorist attack targets in our dataset, such as Government, Military, Education Institutions and so on. We would like to compare the top 10 terrorist attack targets in the first 1970 and the last year 2016 in our dataset. The variation in terrorist attack targets may be related to the policy issues, motivations and religions, etc.

```{r,fig.height=5,fig.width=10, fig.align='center'}
library(gridExtra)
attack1970 <- terrorism[terrorism$iyear==1970, ]
by_target <- attack1970 %>% group_by(targtype1_txt) %>% 
  summarise(n=n())
by_target <- arrange(by_target, desc(n))%>% head(10)

p1<-ggplot(aes(x=reorder(targtype1_txt, n), y=n), data=by_target) +
  geom_bar(stat = 'identity') + ggtitle('Attack Targets, 1970') +
  coord_flip() + theme_fivethirtyeight()

attack2016 <- terrorism[terrorism$iyear==2016, ]
by_target <- attack2016 %>% group_by(targtype1_txt) %>% 
  summarise(n=n())
by_target <- arrange(by_target, desc(n))%>% head(10)

p2<-ggplot(aes(x=reorder(targtype1_txt, n), y=n), data=by_target) +
  geom_bar(stat = 'identity') + ggtitle('Attack Targets, 2016') +
  coord_flip() + theme_fivethirtyeight()

grid.arrange(p1, p2, nrow = 1)
```

The diversity of terrorist attack targets is higher in 2016 than in 1970. The biggest difference is that private citizens and properties become the highest terrorist attack targets in 2016, which does not even appear among the top 10 terrorist attack targets in 1970. This may because the personal hatred is developing rapidly among these years.

For the top 10 terrorist attack targets, they require the most homeland security resources. Policymakers can use these and other results to focus their counter-terrorism measures.

## A heatmap of total number of terrorist attacks worldwide 

To compare the total number of terrorist attacks worldwide, we draw the following two heatmaps. 
```{r}

a <- rle(sort(terrorism1$country_txt))
b <- data.frame(country_txt=a$values, number_of_torrorism_attacks_from_1970_to_1974 = a$lengths)

gtdMap <- joinCountryData2Map( b, 
                               nameJoinColumn="country_txt", 
                               joinCode="NAME" )

#mapDevice('x11')
mapCountryData( gtdMap, 
                nameColumnToPlot='number_of_torrorism_attacks_from_1970_to_1974', 
                catMethod='fixedWidth', 
                numCats=100 )

```

```{r}
a <- rle(sort(terrorism2$country_txt))
b <- data.frame(country_txt=a$values, number_of_torrorism_attacks_from_2012_to_2016 = a$lengths)

gtdMap <- joinCountryData2Map( b, 
                               nameJoinColumn="country_txt", 
                               joinCode="NAME" )

#mapDevice('x11')
mapCountryData( gtdMap, 
                nameColumnToPlot='number_of_torrorism_attacks_from_2012_to_2016', 
                catMethod='fixedWidth', 
                numCats=100 )
```


## Which cities were the most dangerous in  1970-1974 and 2011-2016

Then, we want to explore deeper to see the difference in the most dangerous cities in 1970-1974 and 2011-2016.  They ranked among the world’s most dangerous places on the basis of total number of terrorism attacks.

```{r,fig.height=6,fig.width=9, fig.align='center'}
attack_by_city <- terrorism1 %>% group_by(country_txt, city) %>% 
  summarise(n=n())
attack_by_city <- arrange(attack_by_city, desc(n))
top10_city<- head(attack_by_city, 10)

p1<-ggplot(data=top10_city, aes(x=reorder(city,-n), y=n, group=1)) +
  geom_line()+
  geom_point() + xlab("City") + ylab("Number of terrorist Attacks") +
        ggtitle("Top 10 dangerous city by Year 1970-1974") + theme_fivethirtyeight()

attack_by_city <- terrorism2 %>% group_by(country_txt, city) %>% 
  summarise(n=n())
attack_by_city <- arrange(attack_by_city, desc(n))
top10_city<- head(attack_by_city, 10)

p2<-ggplot(data=top10_city, aes(x=reorder(city,-n), y=n, group=1)) +
  geom_line()+
  geom_point() + xlab("City") + ylab("Number of terrorist Attacks") +
        ggtitle("Top 10 dangerous city by Year 2012-2016") + theme_fivethirtyeight()
grid.arrange(p1, p2, nrow = 2)
```

The most dangeours cities are very different in these two periods. During 1970-1974, the most dangerous cities are in United Kingdom, United States, Argentina, Uruguay and Turkey. Belfast was the most dangerous city in 1970-1974, with approximately 400 terrorist attacks in all.

During 2012-2016, the most dangerous cities are in Iraq, Pakistan, Somalia, Afghanistan, Libya and Yemen. Baghdad was the most dangerous city in 2012-2016, with approximately 4000 terrorist attacks in all. In addition, the total number of attacks increased rapidly, which may be caused by wars and other political issues.







## Terrorist Attacks in XXX by Year in1970-1974 and 2011-2016
```{r}

```

## A heatmap of terrorist attack deaths worldwide in1970-1974 and 2011-2016
```{r}

```


# Executive Summary (focus on quality of presentation choices / techniques)

# Interactive Component 

# Conclusion
