---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
---
1. Introduction (including choice of data, questions), Team description

2. Description of Data

We get the dataset from the Global Terrorism Database (GTD) http://start.umd.edu/gtd/, which is an open-source database including information on terrorist events around the world from 1970 through 2016 (with annual updates planned for the future). Unlike many other event databases, the GTD includes systematic data on domestic as well as international terrorist incidents that have occurred during this time period and now includes more than 170,000 cases. The dataset ends in 2016 because GTD collection beyond 2016 is ongoing and the website is updated annually. They expect to release the 2017 data in Summer 2018. 

In our project, we divide the whole dataset into two subgroups: the data in 1970 to 1974 and 2011-2016. We would like to carry out data visualizatioin and data analysis on these subgroups individually and compare their performances.

For the dataset from 1970-1974, there are 2670 observations of 135 variables. For the dataset from 2011-2016, there are 2670 observations of 135 variables.

The variables include

3. Graphical Analysis of Data Quality


```{r}

library(openxlsx)
terrorism <- read.xlsx("raw data/globalterrorismdb_0617dist.xlsx")

terrorism1<-terrorism[terrorism$iyear<=1974,]

write.csv(terrorism1,"terrorism1.csv")

terrorism2<-terrorism[terrorism$iyear>=2012,]

write.csv(terrorism2,"terrorism2.csv")
```


2. Graphical Analysis of Data Quality

## discover what's in the data file that was exported
```{r}

## choose variables

head(terrorism1)
head(terrorism2)
summary(terrorism1)
summary(terrorism2)
```

## imputations for NULL values 
```{r}

```


##Outlier Analysis and Treatment
```{r}

```

4. Main Analysis (focus on quality of EDA choices / techniques)

countries with the most attack, 1970-1974; 2011-2016
Terrorist Attack Tactics Wordwide, 1970-1974; 2011-2016
Terrorist Attack By Weapon Wordwide, 1970-1974; 2011-2016
Casualties, 1970-1974; 2011-2016
Terrorist Groups with the most Attacks Wordwide, 1970-1974; 2011-2016
Terrorist Attack Targets/Victims , 1970-1974; 2011-2016
Which countries/cities were the most dangerous in  1970-1974 and 2011-2016
Terrorist Attacks in XXX by Year in1970-1974 and 2011-2016
A heatmap of terrorist attack deaths worldwide in1970-1974 and 2011-2016
```{r}

```


5. Executive Summary (focus on quality of presentation choices / techniques)

6. Interactive Component 

7. Conclusion
